Efficient pedigree recording for fast population genetics simulation

### 2018-01-11 forwards_paper.tex
fix 'infer edges' mention

\paragraph{Next steps.}
While these methods work well, and indeed result in significant performance
gains over non-ancestry based simulation, they are far from optimal. Because
forwards time simulation is highly CPU intensive, most simulation engines
are written in C or C++ out of necessity. Therefore, the simplest and most
efficient approach would be to call the \msprime\ C library directly as part of
the core simulation logic, in the manner outlined in Algorithm W. If designed
in this way, the simulation engine would not need to keep copies of the node
and edge information and would not need to infer edges;
even greater gains in computational efficiency could then be obtained. To
facilitate this usage, a standalone, embeddable C library encompassing the core
tree sequence functionality is planned, which should make recording and
outputting tree sequences from any C/C++ code straightforward.

>>>>

\paragraph{Next steps.}
While these methods work well, and indeed result in significant performance
gains over non-ancestry based simulation, they are far from optimal. Because
forwards time simulation is highly CPU intensive, most simulation engines
are written in C or C++ out of necessity. Therefore, the simplest and most
efficient approach would be to call the \msprime\ C library directly as part of
the core simulation logic, in the manner outlined in Algorithm W. If designed
in this way, the simulation engine would not need to keep copies of the node
and edge information (and in the more flexible \simupop{} implementation, would
not need to infer edges);
even greater gains in computational efficiency could then be obtained. To
facilitate this usage, a standalone, embeddable C library encompassing the core
tree sequence functionality is planned, which should make recording and
outputting tree sequences from any C/C++ code straightforward.
